### 2018-02-14 pawpyseed/paper.tex

\subsection{Projection of Pseudowavefunctions onto Partial Waves}

\begin{equation}
e^{i\mathbf{k} \cdot \mathbf{r}} = 4\pi \sum_{l=0}^{\infty}\sum_{m=-l}^{l}
i^l j_l(kr)Y_l^{m*}(\mathbf{\hat{k}})Y_l^m(\mathbf{\hat{r}})
\label{eq:pwexp}
\end{equation}
$\mathbf{r_A} = \mathbf{r} - \mathbf{R_A}$, $\phi_i(\mathbf{r})=R_i(r)Y_l^m(\mathbf{\hat{r}})$,
$\widetilde{\phi}_i(\mathbf{r})=\widetilde{R}_i(r)Y_l^m(\mathbf{\hat{r}})$,
$\mathbf{k'}=\mathbf{k}+\mathbf{G}$\\
$$\widetilde{\psi}_{n\mathbf{k}}=\frac{1}{\sqrt{V}}\sum_{\mathbf{G}}
C_{n\mathbf{k}\mathbf{G}}e^{i\mathbf{k'}\cdot \mathbf{r}}$$
$$\widetilde{\psi}_{n\mathbf{k}}=\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
C_{n\mathbf{k}\mathbf{G}}\sum_{l=0}^{\infty}\sum_{m=-l}^{l}
i^l j_l(k'r_A)Y_l^{m*}(\mathbf{\hat{k'}})Y_l^m(\mathbf{\hat{r}_A})$$
$$\phi_i(\mathbf{r})\widetilde{\psi}_{n\mathbf{k}}=\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
C_{n\mathbf{k}\mathbf{G}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'}
i^{l'} j_{l'}(k'r_A)Y_{l'}^{m'*}(\mathbf{\hat{k'}})Y_{l'}^{m'}(\mathbf{\hat{r}_A})
Y_l^{m*}(\mathbf{\hat{r}}_A)R_i(r_A)$$
$$\braket{\phi_i(\mathbf{r})|\widetilde{\psi}_{n\mathbf{k}}}=
\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2R_i(r_A)j_l(k'r_A)$$
$$\braket{\phi_i-\widetilde{\phi}_i|\widetilde{\psi}_{n\mathbf{k}}}=
\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2(R_i(r_A)-\widetilde{R}_i(r_A))j_l(k'r_A)$$

After the projection is decomposed into a summation over integrals of spherical
Bessel functions, it can be calculated via spherical Bessel transform. This code
uses the fast spherical Bessel transform method NumSBT developed by Talman.\cite{TALMAN}
It runs in $O(NlnN)$ time and works on a logarithmic grid, making it convenient for use with
the POTCAR representations of the partial waves. The resulting logarithmic k-space
grid can be used to calculate the values of the relevant integrals via interpolation.

@@

\section*{Appendix B: Comprehensive POTCAR Guide}
The PAWpySeed module makes use of the POTCAR files provided with the VASP source code, which
contain the projector functions, partial waves, pseudopotentials, and core charge densities
for each element. The format of the POTCAR file is not intuitive to non-developers, so this
appendix seeks to comprehensively document the format of the VASP POTCAR files.

\subsection*{Overview}
A single POTCAR contains the data for one element; a POTCAR file to a multi-element system
is made by simply concatenating elemental POTCAR files. Each PAW POTCAR file follows
the following format.

\begin{enumerate}
	\item
	Settings
	\item
	adsf
	\item
	\textbf{Non local Part}: This section contains the \emph{non local projector functions}.
	The first line after "Non local Part" gives the $l$ quantum number of the projector,
	the number of projectors for that $l$ quantum number, and the radius of the real
	space projector region.
	\begin{enumerate}
		\item
		\textbf{Reciprocal Space Part}: The reciprocal space projection operator.
		\item
		\textbf{Real Space Part}: The real space projection operator values on a radial
		grid. The radius at a given index $I$ is $RMAX*I/NDATA$, where RMAX and NDATA
		are given in the settings section. Since $I$ is 0-indexed, the true maximal
		radius of the projector is actually $RMAX*(NDATA-1)/NDATA$. Unlike the
		\emph{partial wave} values (see \textbf{pseudo wavefunction},
		the projector values are not mulitplied by $r$.
		$$p(\mathbf{r})=realspacepart(index)Y_l^m(\hat{\mathbf{r}})$$
	\end{enumerate}
	\item
	PAW Radial Sets
	\begin{enumerate}
		\item
		Augmentation charges
		\item
		Occupancies
		\item
		\textbf{grid}: The exponential grid on which calculations related
		to the \emph{partial waves} are performed.
		\item
		\textbf{pseudo wavefunction}: A pseudo \emph{partial wave} on the provided
		radial grid, multiplied by $r$ for easy radial integration. I.e.
		$$\phi(\mathbf{r}(index))=\frac{pseudowavefunction(index)}{r(index)}Y_l^m(\hat{\mathbf{r}})$$
		Listed in the same order as the projector functions.
		\item
		\textbf{ae wavefunction}: Same pseudo wavefunction, but for the all electron \emph{partial wave}.
	\end{enumerate}
\end{enumerate}

\subsection*{}

>>>>

@@

\section*{Appendix B: Comprehensive POTCAR Guide}
